Lens Modeling in \sw

### 2013-12-12 text/tex/results.tex
final changes

The second test was to compare the mass distribution of the lens $\kappa(x, y)$ of the models and the sims.
To get a means of comparing the sims to the models, the total convergence, also called enclosed mass $\kappa_{\text{encl}}(r)$ was calculated for both.
The Einstein radius $\Theta_E$ is defined by $\kappa_{\text{encl}}(\Theta_E)=1$ and gives a number that allows the comparison between a sim and a model.
We also let an expert (PS) model three selected systems to compare the results from volunteers to those of a professional.

To compare the enclosed mass profile and the Einstein radius of the simulation and the models, \kenc was calculated using the mass map \kap[x,y] generated in the modeling process.
From the ensemble of models generated by one modeling process, the mean is taken as the resulting $\kappa(r)$ to calculate $\theta_E$.
To estimate the errors, also the extremal models are used to estimate a lower and upper limit for $\theta_E$.
These results can be seen in \figref{ER_all_models}.
This figure shows that this technique of estimating the error minimizes the error significantly and should be improved for further analysis.

In \figref{ER_per_sim} can be seen, that the calculated \ERf of the models tend to be too high.
The overshoot varies from around 0.2 to 0.4 for good models.
One of the reasons for this is, that it's hard to get the center of the lens on spot.
An offset leads to a flatter mass profile for the model compared to the simulation.

@@

Two additional sims were modeled by an expert, \asw{1hpf} and \asw{0vqg}.
Looking at the results for \ERg for those models in \figref{ER_per_sim}, we conclude that the performance of volunteers (blue crosses) and experts (red crosses, offset) is comparable.
Note that the models of \asw{0vqg} with \ERg[, rel] around 0.25 (6935 -- 6937) are failed models that show the attempts of a single user, that came finally up with model 6938 as final result.\todo{remove?}

>>>>

The second test was to compare the mass distributions of the lens $\kappa(x, y)$ given by the sims and generated by the volunteers.
To get a means of comparing the sims to the models, the total convergence\footnote{often called enclosed mass} $\kappa_{\text{encl}}(r)$ was calculated for both.
The Einstein radius $\Theta_\text{E}$ is defined by $\kappa_{\text{encl}}(\Theta_\text{E})=1$ and gives a number that allows a rough comparison between a sim and a model.
We also let an expert (PS) model three selected systems to compare the results from volunteers to those of a professional.

To compare the enclosed mass profile and the Einstein radius of the simulation and the models, \kenc was calculated using the mass map \kap[x,y] generated in the modeling process.
From the ensemble of models generated by one modeling process, the mean is taken as the resulting $\kappa(r)$ to calculate \ERg.
To estimate the errors, the extremal models are used to estimate a lower and upper limit for \ERg.
These results can be seen in \figref{ER_all_models}.
This figure shows that this technique of estimating the error using the ensemble of all models underestimates the error significantly and should be improved for further analysis.

\Figref{ER_per_sim} shows that the calculated \ERf of the models tend to be too high.
The overshoot varies from around 0.2 to 0.4 for good models.
One of the reasons for this is that it is hard to get the center of the lens on spot.
An offset leads to a flatter mass profile for the model compared to the simulation.

@@

Two additional sims were modeled by an expert, \asw{1hpf} and \asw{0vqg}.
Looking at the results for \ERg for those models in \figref{ER_per_sim}, we conclude that the performance of volunteers (blue crosses) and experts (red crosses, offset) is comparable.
%Note that the models of \asw{0vqg} with \ERg[, rel] around 0.25 (6935 -- 6937) are failed models that show the attempts of a single user, that came finally up with model 6938 as final result.\todo{remove?}
